---
title: "autocorrelation analysis"
author: "Sunse Kwon"
date: '2022-11-20'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Import relevant packages
```{r}
require(nonlinearTseries)
require(crqa)
require(casnet)
require(tseriesChaos)
require(plot3D)
require(scatterplot3d)
require(rgl)
require(ggplot2)
require(Hmisc)

# Turn off scientific notation
options(scipen=999)
```

## Read dataset
```{r}
data <- read.csv('data_droped_nov18_dummy_final.csv')
```


## Subsetting individual parking lot
```{r}
carpark_sub <- data[data$carpark_number == 0,]
```


## Conduct autocorrelation analysis during EDA stage

### Entire dataset (855 parking lots)
```{r}
tau.acf <- timeLag(data$lots_available, technique = "acf", lag.max = 100, do.plot = T)
print(tau.acf)
```
with entire dataset, autocorrelation function returns the relevant timelag value is 1 (15 minute).

### Individual level (single parking lot)
```{r}
carpark_sub.acf <- timeLag(carpark_sub$lots_available, technique = "acf", lag.max = 100, do.plot = T)
print(carpark_sub.acf)
```
with single dataset, autocorrelation function returns the relevant timelag value is 16 (4 hour). 


with this result, study tested 3 time window sizes specified below.

* window 1 : used 1 previous timestep(15 minute) to predict next value in future.
* window 2 : used 4 previous timesteps(1 hour) to predict next value in future.
* window 3 : used 16 previous timesteps(4 hour) to predict next value in future.
